TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults

### 2023-01-23 paper/manuscript_submission1.Rmd
prepare repo for revision

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "6856"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "6856"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---
